Capitalized Title Here

### 2017-01-20 writing/r_journal_draft/anderson-eddelbuettel.Rmd
Add directory for R Journal version of write-up

---
title: "Setting up drat repo for a data package"
author: "Brooke Anderson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Motivation

@@

# Posting data package to a drat repository

@@

# Setting up a CRAN package to use the data package

>>>>

---
title: Capitalized Title Here
author:
  - name: G. Brooke Anderson
    affiliation: Colorado State University
    address:
    - Lake Street
    - Fort Collins, CO
    email:  brooke.anderson@colostate.edu
  - name: Dirk Eddelbuettel
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author2@work
abstract: >
  An abstract of less than 150 words.
preamble: >
  % Any extra latex you need in the preamble
output: rticles::rjournal_article
---

## Motivation

@@

## Posting data package to a drat repository

@@

## Setting up a CRAN package to use the data package
